---
title: "hw2"
output: html_document
date: "2022-10-16"
name: "Nathan De Los Santos"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidymodels)
library(ISLR)
library(corrplot)
library(ggthemes)
library(ggplot2)
abalone_data <- read.csv('data/abalone.csv')
```

## Question 1
```{r}
abalone <- abalone_data %>%
  mutate(age = abalone_data$rings + 1.5)

abalone %>%
  ggplot(aes(age)) +
  geom_histogram(bins = 60)
```
Using a bin size of 60, we can see that the distribution of age in the abalone data set is slightly skewed to right. Most abalone ages are around 11.5 years old. 


## Question 2
```{r}
set.seed(777)

abalone_split <- initial_split(abalone, prop = 0.7)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
```

## Question 3
```{r}
abalone_recipe <- recipe(age ~ type + longest_shell + diameter + height + whole_weight + shucked_weight + viscera_weight + shell_weight, data = abalone_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms = ~ type_M:shucked_weight) %>%
  step_interact(terms = ~ longest_shell:diameter) %>%
  step_interact(terms = ~ shucked_weight:shell_weight) %>%
  step_center(all_nominal_predictors()) %>%
  step_scale(all_nominal_predictors())
```



## Question 4
```{r}
lm_model <- linear_reg() %>%
  set_engine("lm")
```

## Question 5
```{r}
lm_wflow <- workflow() %>%
  add_model(lm_model) %>%
  add_recipe(abalone_recipe)
```

## Question 6
```{r}
lm_fit <- fit(lm_wflow, abalone_train)

predict(lm_fit, data.frame(type = "F", longest_shell = 0.5, diameter = 0.1, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1))
```

## Question 7
```{r}
library(yardstick)

abalone_metrics <- metric_set(rmse, rsq, mae)
abalone_train_res <- predict(lm_fit, new_data = abalone_train)
abalone_train_res <- bind_cols(abalone_train_res, abalone_train)
abalone_metrics(abalone_train_res, truth = age, estimate = .pred)
```
We recorded an $R^s$ of 0.5539742, so only about half of the variance can be predicted/explained by the model. Therefore, this is not the greatest model to use to predict the age of an abalone.